DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-01 paper/overview.tex
Add side-by-side pictures of tracks
revision

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

@@

Other issues we observed in training/testing the network, which
can affect the prediction accuracy of the CNN, are camera and actuator
(motor) control latencies. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. This time can be noticable depending on the camera 
used and the performance of the Pi. Higher camera latency could
negatively affect control performance, because the DNN would analyze
stale scenes. Actuator (motor) control latency also can be a
factor, because moving the sterring motor to a desired position takes
time. 
In our platform, the combined latency is measured to be around
50 ms. In other words, in the recorded video and control data, a
control action (left, center, right) taken by the CNN appears to be
applied 50 ms later. Considering that camera's framerate is 30Hz
(33.3ms/frame), this is about two frames after the control action.
%% We experimentally measured the camera
%% latency and found it to be around 50-100 ms.
If this value is too high, control performance may suffer. 
For reference, the latency of human perception is known to be as fast
as 13 ms~\cite{ThomasBurger2015}.
% https://www.pubnub.com/blog/2015-02-09-how-fast-is-realtime-human-perception-and-technology/

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. In our testing, we found that the
DeepPicar could remain on a fairly challenging track for over 10
minutes at a moderate speed (50\% throttle), at which point we stop
the experiment, and more than one minute at a higher speed (75\%
throttle)~\footnote{A collection of self-driving videos can be found
  at: \url{https://photos.app.goo.gl/ce93sU7jPk4ywO8u2}}. Running at
higher speed is inherently more challenging because the CNN controller
has less time to recover from mistakes (bad predictions).

>>>>

\begin{figure}[h]
  \centering
%% <<<<<<< HEAD
%%   \includegraphics[width=.5\textwidth]{figs/track_new2}
%%   \caption{One of the custom tracks used for training/testing.}
%%   \label{fig:track}
%% =======
  \begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{figs/track_new2}
    \caption{Track 1.}
    \label{fig:track}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.52\textwidth}
    \includegraphics[width=\textwidth]{figs/track-2}
    \caption{Track 2.}
    \label{fig:track2}
  \end{subfigure}
  \caption{Custom tracks used for training/testing}
  \label{fig:tracks}
%% >>>>>>> f3814396d8701264f2439b42fbe8bbb608c41452
\end{figure}

@@

Other issues we observed in training/testing the network, which
can affect the prediction accuracy of the CNN, are camera and actuator
(motor) control latencies. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. This time can be noticable depending on the camera 
used and the performance of the Pi. Higher camera latency could
negatively affect control performance, because the DNN would analyze
stale scenes. Actuator (motor) control latency also can be a
factor, because moving the sterring motor to a desired position takes
time. 
In our platform, the combined latency is measured to be around
50 ms. In other words, in the recorded video and control data, a
control action (left, center, right) taken by the CNN appears to be
applied 50 ms later. Considering that camera's framerate is 30Hz
(33.3ms/frame), this is about two frames after the control action.
%% We experimentally measured the camera
%% latency and found it to be around 50-100 ms.
If this value is too high, control performance may suffer.
Our initial prototype suffered this problem as the observed camera and
control latency was as high as 300 ms, which negatively affected
control performance.
For reference, the latency of human perception is known to be as fast
as 13 ms~\cite{ThomasBurger2015}. 
% https://www.pubnub.com/blog/2015-02-09-how-fast-is-realtime-human-perception-and-technology/

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. In our testing, we found that the
DeepPicar could remain on a fairly challenging track for over 10
minutes at a moderate speed (50\% throttle), at which point we stop
the experiment, and more than one minute at a higher speed (75\%
throttle)~\footnote{A collection of self-driving videos can be found
  at: \url{https://photos.app.goo.gl/ce93sU7jPk4ywO8u2}}. Running at
higher speed is inherently more challenging because the CNN controller
has less time to recover from mistakes (bad predictions).  Also, we
find that the prediction accuracy is significantly affected by the
quality of training data as well as various environmental factors such
as the lighting condition. We plan to investigate more systematic ways
to improve the CNN's prediction accuracies.
